Cost-Benefit Analysis

### 2023-04-25 workflow/notebooks/cost-benefit-analysis.Rmd
TODO: evaluate models with number needed to benefit

@@

@@

## [mich med treatment guidelines](https://www.med.umich.edu/1info/FHP/practiceguides/InptCDiff/C-Diff.pdf)

>>>>

## evaluating ml models

[number needed to benefit](https://academic.oup.com/jamia/article-abstract/26/12/1655/5516459)

> In the simplest terms, prediction can be distilled into an NNS and action into a number needed to treat. When contextualized within this framework, the product of NNS and number needed to treat results in a number needed to benefit. The table outlines key variables in this framework that will alter the estimated number needed to benefit across different modeling and implementation scenarios.

@@

**from 2008, now out of date**

@@

### [idsa treatment guidelines comparison](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC9780550/)

i may need to also consider "fulminant" cdi criteria

### [mich med treatment guidelines](https://www.med.umich.edu/1info/FHP/practiceguides/InptCDiff/C-Diff.pdf)
